Insights Into Computational Reproducibility in Plant Pathology and a Way Forward

### 2021-06-14 analysis/paper/paper.Rmd
Fix link formatting

At the second level, Lehner et al. [-@Lehner2017] used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean tied ([<https://emdelponte.github.io/paper-white-mold-meta-analysis/>](https://emdelponte.github.io/paper-white-mold-meta-analysis/){.uri}). The website clearly demonstrates the analysis for readers and uses R so that anyone can easily replicate the work. Likewise, Duku et al. [-@Duku2016] provide scripts for models, data and code for graphs, via a website hosted by GitHub, [<http://adamhsparks.github.io/MICCORDEA/>](http://adamhsparks.github.io/MICCORDEA/){.uri}, that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.

@@

The fourth level includes packaging the analysis as a software package, _e.g._, R Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as Khaliq et al. [@Khaliq2020] have done. Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of *Ascochyta rabiei* conidia dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a]. When this level is employed, tools such as Binder, [<https://mybinder.org>](https://mybinder.org){.uri}, can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al. used [-@Miorini2018, [-@Miorini2019]]. Kamvar et al. [-@Kamvar2015] took a slightly different approach by including all files necessary for the analysis and most output files in a repository [@Kamvar2014] that also included an installable R package that was used for the original analysis.
While there are many other methods, these two approaches illustrate some of the best-practices where the data and other files were deposited in repositories with DOIs and reproducibility issues were addressed by using R packages to handle dependencies and other versioning issues making the work more portable.

@@

To make your data the most widely usable, ensure that it has a persistent identifier.
A digital object identifier (DOI) is the most common ([<https://www.doi.org/>](https://www.doi.org/){.uri}) but handle is also an option ([<https://handle.net/>](https://handle.net/){.uri}).
There are different options for generating a DOI for your data and other materials.
FigShare, Zenodo and OSF all offer long-term archival along with a service to generate a DOI for your materials.
The use of a persistent identifier works to ensure that even if the data are moved, they can still be located using that unique identifier.
For more on FAIR data, visit Go-Fair [<https://www.go-fair.org/fair-principles/>](https://www.go-fair.org/fair-principles/){.uri}.

>>>>

At the second level, Lehner et al. [-@Lehner2017] used GitHub to host a code repository of their research compendium website with data and a reproducible report that explains in detail all steps of the analysis and the R code for conducting a meta-analysis for assessing heterogeneity in the relationship between white mold incidence and soybean yield and between incidence and soybean tied ([https://emdelponte.github.io/paper-white-mold-meta-analysis/](https://emdelponte.github.io/paper-white-mold-meta-analysis/)). The website clearly demonstrates the analysis for readers and uses R so that anyone can easily replicate the work. Likewise, Duku et al. [-@Duku2016] provide scripts for models, data and code for graphs, via a website hosted by GitHub, [http://adamhsparks.github.io/MICCORDEA/](http://adamhsparks.github.io/MICCORDEA/), that can be used to replicate their study modelling the effects of climate change on rice bacterial blight and rice leaf blast in Tanzania.

@@

The fourth level includes packaging the analysis as a software package, _e.g._, R, Julia or Python package at a minimum, with the use of continuous integration and possibly a software container like Docker as Khaliq et al. [@Khaliq2020] have done. Their research compendium provides a Docker instance, DOI and full R package that enable readers to fully replicate their analysis of *Ascochyta rabiei* conidia dispersal in chickpea using the data collected and stepping through other points where weather data were investigated and various models were fit before deciding on the best fit and recreate any figures as published in the article [@Khaliq2020a]. When this level is employed, tools such as Binder, [https://mybinder.org](https://mybinder.org), can be used that allow readers and reviewers to launch an interactive session in their web browser and interact with the data and rerun the analysis in an RStudio instance or Jupyter notebooks as Mioroni et al. used [-@Miorini2018, [-@Miorini2019]]. Kamvar et al. [-@Kamvar2015] took a slightly different approach by including all files necessary for the analysis and most output files in a repository [@Kamvar2014] that also included an installable R package that was used for the original analysis.
While there are many other methods, these two approaches illustrate some of the best-practices where the data and other files were deposited in repositories with DOIs and reproducibility issues were addressed by using R packages to handle dependencies and other versioning issues making the work more portable.

@@

To make your data the most widely usable, ensure that it has a persistent identifier.
A digital object identifier (DOI) is the most common ([https://www.doi.org/](https://www.doi.org/)) but handle is also an option ([https://handle.net/](https://handle.net/)).
There are different options for generating a DOI for your data and other materials.
FigShare, Zenodo and OSF all offer long-term archival along with a service to generate a DOI for your materials.
The use of a persistent identifier works to ensure that even if the data are moved, they can still be located using that unique identifier.
For more on FAIR data, visit Go-Fair [https://www.go-fair.org/fair-principles/](https://www.go-fair.org/fair-principles/).
